Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-06-18 paper/IJCAI19/paper.tex
closes #5#

\author{
Sofia Reis$^1$
\and
Rui Abreu$^1$\and
Marcelo d'Amorim$^2$\affiliations
$^1$IST, University of Lisbon \& INESC-ID, Portugal\\
$^2$Federal University of Pernambuco, Brazil\\
\emails
sofia.o.reis@tecnico.ulisboa.pt,
rui@computer.org; damorim@cin.ufpe.br\\
}

>>>>

\author{
Sofia Reis$^1$
\and
Rui Abreu$^1$ \textnormal{and}
Marcelo d'Amorim$^2$\affiliations
$^1$IST, University of Lisbon \& INESC-ID, Portugal\\
$^2$Federal University of Pernambuco, Brazil\\
\emails
sofia.o.reis@tecnico.ulisboa.pt,
rui@computer.org; damorim@cin.ufpe.br\\
}
